\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}

\title{Academic Vibing: Consensus Divergence Index as a Signal for Multi-Model Disagreement}
\author{Attogram}
\date{June 2026}

\begin{document}

\maketitle

\begin{abstract}
Academic Vibing is a meta-methodology for high-speed, agentic research where rigor emerges through architectural diversity and adversarial auditing. This paper synthesizes a longitudinal n=1 study (96-hour, 5-paper sprint) documenting the \textbf{Consensus Divergence Index (CDI)}—a robust metric for identifying model sycophancy and shared training-data bias in Multi-Agent Systems (MAS). We demonstrate that the methodology is effective on consumer-grade hardware (16GB Macbook) using accessible cloud-based inference, proving that high-signal research can be conducted without massive local compute resources. By focusing on multi-model disagreement rather than agreement, researchers can identify high-signal research boundaries and improve intellectual integrity.
\end{abstract}

\section{Introduction}
Academic Vibing prioritizes ``Structured Curiosity'' over traditional linear research pipelines. It is designed for low-latency technical environments where the Human Bottleneck is mitigated by a \textbf{Recursive Agent Consensus (RAC)}. We explicitly validate the feasibility of this approach on consumer hardware (Claim 13), using a mobile-first stack.

\section{Methodology: Adversarial Rigor via CDI}
Rigor is defined by the measurement of friction. The CDI is calculated as the ratio of disputed claims to total claims across a model swarm. A high CDI serves as a signal for authentic research boundaries, while a low CDI warns of a ``Consensus Trap.''

\section{The Leapfrog Mechanism: Context Persistence}
By externalizing research state into a structured GitHub Issue-Loop, the methodology decouples context operations. This reduces task re-entry costs and allows for non-linear research workflows that are more resilient to interruptions than traditional methods.

\section{Epistemic Triage: Two-Stream Architecture}
We enforce a strict dual-channel workflow to maintain academic integrity: Stream 1 (P1 - Canonical Paper) for falsifiable claims, and Stream 2 (PLG0 - The Outlet) for generative exploration. No artifacts from the generative stream enter the canonical paper without formal re-derivation.

\section{Conclusion}
Future work focuses on the formalization of the ``Endorsement Gate'' for arXiv category authorization. The CDI provides a robust framework for independent researchers to navigate the complexities of Multi-Agent research.

\begin{thebibliography}{9}
\bibitem{extendedmind} Clark, A. \& Chalmers, D.J. (1998). The Extended Mind. Analysis, 58, 7-19.
\bibitem{cognitionwild} Hutchins, E. (1995). Cognition in the Wild. MIT Press.
\bibitem{interruption} Mark, G., Gudith, D. \& Klocke, U. (2008). The cost of interrupted work: More speed and stress. CHI 2008.
\end{thebibliography}

\end{document}
